Data Management for LSST Special Programs

### 2024-03-01 sec_proc.tex
caps LSE

\textbf{How Main Survey and Special Program data would co-exist.}
No ``unique and separate" data products for the Special Progams would be 
produced by regular Prompt processing.
Special Programs data that is processed by the Prompt pipeline would 
contribute to the Prompt data products for the Main Survey as 
described in Section 3 of the DPDD \citedsp{lse-163}. 
These data products are the results of Difference Image Analysis (DIA),
such as the difference images, catalogs of sources detected in difference
images ({\tt DiaSources}) and associated static-sky {\tt DiaSources}
into {\tt DiaObjects}, and alert packets.
Including visits from Special Programs in regular Prompt processing alongside
vists from the Main Survey is not, in general, anticipated to affect Main Survey 
or WFD-specific science goals.
For example, analyses for a WFD-only subset could still be done using the observing mode
and region labels described in Section~\ref{ssec:sci_labels}, which would be
propogated to difference images, difference-image catalogss, and alerts.

>>>>

\textbf{How Main Survey and Special Program data would co-exist.}
No ``unique and separate" data products for the Special Progams would be 
produced by regular Prompt processing.
Special Programs data that is processed by the Prompt pipeline would 
contribute to the Prompt data products for the Main Survey as 
described in Section 3 of the DPDD \citedsp{LSE-163}. 
These data products are the results of Difference Image Analysis (DIA),
such as the difference images, catalogs of sources detected in difference
images ({\tt DiaSources}) and associated static-sky {\tt DiaSources}
into {\tt DiaObjects}, and alert packets.
Including visits from Special Programs in regular Prompt processing alongside
vists from the Main Survey is not, in general, anticipated to affect Main Survey 
or WFD-specific science goals.
For example, analyses for a WFD-only subset could still be done using the observing mode
and region labels described in Section~\ref{ssec:sci_labels}, which would be
propogated to difference images, difference-image catalogss, and alerts.
